Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-28 leadership_across_cultures_contexts.Rmd
Minor edit

---
title: "Leader functions and qualities across 59 cultures: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
---

@@

```{r cluster, fig.cap="Cluster analysis of leader quality variables (left) and leader function variables (right). Distances are $1 - cor$. Ward agglomeration method. p-values computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
# plot(m_pvclust_qual)
# pvrect(m_pvclust_qual, alpha = 0.9)
knitr::include_graphics("Figures/m_pvclust.both.png")
```

>>>>

---
title: "Leader functions and qualities across 59 cultures: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
csl: evolution-and-human-behavior.csl
---

@@

```{r cluster, fig.cap="Cluster analysis of leader quality variables (left) and leader function variables (right). Distances are $1 - cor$. Ward agglomeration method. AU p-values (red) computed with 10,000 bootstrap samples using the pvclust package [@pvclust2015]."}
# plot(m_pvclust_qual)
# pvrect(m_pvclust_qual, alpha = 0.9)
knitr::include_graphics("Figures/m_pvclust.both.png")
```
